---
title: "LLC1 (3 Batchs)+ CT26 (2 Batchs)"
author: "Siwakorn"
date: "2023-03-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(Seurat)
library(tidyverse)
library(harmony)
```

```{r}
col_orange =  c("grey","yellow","orange","red")

scale_orange = scale_color_gradientn(colours = c("grey","yellow","orange","red"), values = c(0,0.1,0.5,1))
scale_ig = scale_color_gradientn(colours = c("grey","#120078","#9d0191","#fd3a69","#fecd1a"), values = c(0,0.1,0.3,0.6,1))
scale_viridis = scale_color_gradientn(colours = c("grey",c(viridis::viridis(6))[1:5],"#fecd1a" ) )
Dot_axis90A = theme(axis.text.x =  element_text(size = 15, angle = 90, hjust = 1, vjust = 0.3,color = "black",face ="italic"), axis.text.y = element_text(size = 15,color = "black")) 

Clustering1 <- function(tmp,dim=30,res=0.3,spread =1, dist = 0.5,group = "ID" ){
      DefaultAssay(tmp) = "RNA"
      tmp <- NormalizeData(tmp) %>% FindVariableFeatures() %>% ScaleData() %>% RunPCA(verbose = FALSE)
      tmp <- RunHarmony(tmp, group.by.vars = group)
      tmp <- RunUMAP(tmp, reduction = "harmony", dims = 1:dim, min.dist = dist, spread = spread )
      tmp <- FindNeighbors(tmp, reduction = "harmony", dims = 1:dim) %>% FindClusters(resolution = res)
      return(tmp)
}
```

```{r}
geneSet = list()
geneSet$Markers.Lineage = c("Ptprc","Cd3d","Nkg7","Csf1r","Csf3r","Ms4a1","Cd19","Igkc","Mki67","Col1a1","Kit","Hdc","Col1a1","Col1a2","Ccl8",'Col3a1',"Col18a1","Col4a1")
geneSet$Markers <- c(
                   "Ncr1","Klra3","Fcer1g","Gzma","Nkg7","Gzmb","Prf1","Klr8","Il2rb","Xcl1",
                   "Cd3d","Trac","Trbc1","Trbc2","Cd8a","Cd8b1","Pdcd1","Ifng","Tox","Havcr2","Tcf7",
                   "Cd4","Icos","Foxp3","Ctla4","CD274","Tnfrsf9","Tnfrsf18",
                   "Trdc",
                   "Cd79b","Cd19","Ms4a1","Igkc","Ighd","Ighm",
                   "Csf1r","C1qa","Adgre1","C1qa","Ccl7","Ccl12","Apoe","Axl",
                   "Vcan","Il1b","Cxcl1","Spp1","Cxlc2","Cxcl1","Tgfbi", "Arg1","Vegfa","Cd274","Egln3","Gpnmb",
                   "Irf7","Ifi203","Mx1","Cxcl10","Fcgr1",
                   "Csf3r","S100a8","S100a9","Cxcl3","Retnlg","Il1r2","Il1f9","Arg2","Cxcr2","Csf3","Hcar2","Cxcl2","Il1b","Isg15",
                   "H2-Ab1","H2-Eb1","H2-DMb1","H2-Oa","H2-DMb2",
                   "Xcr1","Itgae","Btla",
                   "Itgax","Cd74","Cd209a","Ccl17",
                   "Ccr7","Ccl5","Il12b","Il4i1","Ccl22","Ly75",
                   "Clec10a","Gpr171","Siglech","Ccr9","Iglc3","Cd300c",
                   "Mki67","Hist1h3c","Cdca8","Hmgb1"
                   ) %>% intersect(rownames(LC))
geneSet$Markers.TNK = c("Cd3e","Cd4","Cd8a","Nkg7","Foxp3","Trdc","Tcrg-C4","Klra5","Tcrg-C1","Il2ra","Mki67","Igkc","Isg15","Csf3r","percent.mt")
geneSet$Markers.Myeliod = c("Csf1r","Csf3r","Adgre1","C1qa","C1qb","Axl","Mertk","Mrc1","Ptgs2","Ptger2","Vcan","Il1b","Ptgs1","Ptger4","Vegfa","Spp1","Isg15","Ifit1","Mki67",
                            "Arg1","H2-Ab1","H2-Eb1","H2-Oa","H2-DMb1","H2-DMb2",
                            "Itgax","Itgam","Clec9a","Xcr1","Lamp3","Ccr7","Clec10a","Siglech",
                            "Igkc","Malat1")
```

#Initiation
```{r}
library(Seurat)
library(SeuratWrappers)
library(harmony)
library(tidyverse)
options(future.globals.maxSize = 100000 * 1024^2)

Clustering1 <- function(tmp,dim=30,res=0.3,spread =1, dist = 0.5,group = "ID" ){
      DefaultAssay(tmp) = "RNA"
      tmp <- NormalizeData(tmp) %>% FindVariableFeatures() %>% ScaleData() %>% RunPCA(verbose = FALSE)
      tmp <- RunHarmony(tmp, group.by.vars = group)
      tmp <- RunUMAP(tmp, reduction = "harmony", dims = 1:dim, min.dist = dist, spread = spread )
      tmp <- FindNeighbors(tmp, reduction = "harmony", dims = 1:dim) %>% FindClusters(resolution = res)
      return(tmp)
}

Batch = c(rep("Day6",6),rep("Day1.5",6),rep("Day14",5))
Condition = c("Control","Control","EP2i","EP4i","EP2iEP4i","EP2iEP4i",
	      "Control","Control","Control","EP2iEP4i","EP2iEP4i","EP2iEP4i", 
              "Control","Control","Depletion","Depletion","EP2iEP4i" )
ID =  c("Day6_Control1","Day6_Control2","Day6_EP2i","Day6_EP4i","Day6_EP2iEP4i1","Day6_EP2iEP4i2",
        "Day1.5_Control1","Day1.5_Control2","Day1.5_Control3","Day1.5_EP2iEP4i1","Day1.5_EP2iEP4i2","Day1.5_EP2iEP4i3",
        "Day14_Control1","Day14_Control2","Day14_DT1","Day14_DT2","Day14_EP2iEP4i")

data.dir = c(
      "//home/siwakorn/LLC/CountMatrix/scRNA1_no1/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA1_no2/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA1_no3/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA1_no4/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA1_no5/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA1_no6/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA2_no1/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA2_no2/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA2_no3/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA2_no4/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA2_no5/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA2_no6/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA3_no1/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA3_no2/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA3_no3/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA3_no4/filtered_feature_bc_matrix/",
      "//home/siwakorn/LLC/CountMatrix/scRNA3_no6/filtered_feature_bc_matrix/")

LLC <- list()

for(i in 1:length(data.dir)){
      print(ID[i])
      tmp = Read10X(data.dir = data.dir[i]  )
      tmp1 = rownames(tmp)
      tmp1 = gsub("mm10___","",tmp1)
      rownames(tmp) = tmp1
      LLC[[i]] <- CreateSeuratObject(counts = tmp, project = "LLC1", min.cells = 3, min.features = 0)
      LLC[[i]][["percent.mt"]] <- PercentageFeatureSet(LLC[[i]], pattern = "^mt-")
      LLC[[i]]$CB.original = colnames(LLC[[i]])
      LLC[[i]]$Batch = Batch[i]
      LLC[[i]]$Condition <- Condition[i]
      LLC[[i]]$ID <- ID[i]
      LLC[[i]]$CB.new = paste0("LLC1_",LLC[[i]]$ID,":", colnames(LLC[[i]]) )
      LLC[[i]]$CB.new = gsub("-1","x",LLC[[i]]$CB.new)
      LLC[[i]] <- RenameCells(LLC[[i]], new.names = LLC[[i]]$CB.new )
}
saveRDS(LLC, file = "//home/siwakorn/Mouse/RDS/LLC.230328.rds")

print("Merging1")

tmp <- merge(x = LLC[[1]],
		       y = LLC[2:length(LLC)],
		       merge.data = TRUE)
LLC = tmp 
tmp = 0


print("CT26")

Batch = c(rep("Batch1",3),rep("Batch2",2),rep("Batch1",3),rep("Batch2",6))
Condition = c(rep("Control",5),rep("EP4i",5),"PD1i","PD1i","PD1iEP4i","PD1iEP4i")
ID = c(paste0("Control",1:5),
         paste0("EP4i",1:5),
         "PD1i1","PD1i2","PD1iEP4i1","PD1iEP4i2")

CellRangerDir = paste0("//home/siwakorn/CT26/Counts/",ID, "/filtered_feature_bc_matrix")
CT26 = list()
for(i in 1:length(CellRangerDir)){
      print(ID[i])
      tmp = Read10X(data.dir = CellRangerDir[i]  )
      CT26[[i]] <- CreateSeuratObject(counts = tmp,project = "CT26", min.cells = 3, min.features = 0)
      CT26[[i]][["percent.mt"]] <- PercentageFeatureSet(CT26[[i]], pattern = "^mt-")
      CT26[[i]]$CB.original = colnames(CT26[[i]])
      CT26[[i]]$Batch = Batch[i]
      CT26[[i]]$Condition <- as.character(Condition[i])
      CT26[[i]]$ID <- as.character(ID[i])
      CT26[[i]]$CB.new = paste0("CT26_",CT26[[i]]$ID, ":", colnames(CT26[[i]]) )
      CT26[[i]]$CB.new = gsub("-1","x",CT26[[i]]$CB.new)
      CT26[[i]] <- RenameCells(CT26[[i]], new.names = CT26[[i]]$CB.new )
}
saveRDS(CT26, file = "//home/siwakorn/Mouse/RDS/CT26.230328.rds")
print("Merging2")
tmp <- merge(x = CT26[[1]],
		       y = CT26[2:length(CT26)],
		       merge.data = TRUE)
CT26 = tmp 
tmp = 0

RNA = merge(LLC,CT26)
LLC = 0
CT26 = 0
gc()

print("Integration")
RNA = NormalizeData(RNA) %>% FindVariableFeatures() %>% ScaleData() %>% RunPCA(verbose = FALSE)
RNA = RunHarmony(RNA, group.by.vars = "ID" )

saveRDS(RNA, file = "//home/siwakorn/Mouse/RDS/LC.230328.Unfilter.rds")

RNA = subset(RNA, percent.mt < 10)
RNA = Clustering1(RNA)
saveRDS(RNA, file = "//home/siwakorn/Mouse/RDS/LC.230328.QC.rds")

```

```{r}
LC = readRDS(file = "//home/siwakorn/Mouse/RDS/LC.230328.QC.rds")
```

```{r}
DimPlot(LC, label =T)
for(i in c("Ptprc","Cd3d","Cd8a","Foxp3","Nkg7","Csf1r","Csf3r","Igkc","Mki67","Hdc") ){
      print(FeaturePlot(LC,i))
}
```

#Identity.Celltype
```{r,fig.width=16, fig.height=6}
DotPlot(LC,features = geneSet$Markers) + Dot_axis90A + scale_viridis

```

```{r}
LC = RenameIdents(LC,
                  '3' = "TNK",
                  '8' = "TNK",
                  '10' = "TNK",
                  '14' ="TAN",
                  '4' = "TAN",
                  '0' = "Myeloid",
                  '1' = "Myeloid",
                  '2' = "Myeloid",
                  '9' = "DC",
                  '11' = "DC",
                  '12' = "DC",
                  '15' = "DC",
                  '18' = "B_cell",
                  '5' = "Dividing",
                  '17' = "Dividing",
                  '6' = "Fibroblast",
                  '7' = "Minor",
                  '13' = "Minor",
                  '16' = "Minor",
                  '19' = "Minor",
                  '20' = "Minor"
                  )
LC$Identity.Lineage = Idents(LC)
saveRDS(LC, file = "//home/siwakorn/Mouse/RDS/LC.230329.rds")
LC = readRDS(file = "//home/siwakorn/Mouse/RDS/LC.230329.rds")

TNK = subset(LC, idents = "TNK")
M = subset(LC, idents = c("Myeloid","DC") )
Div = subset(LC, idents = "Dividing")


TNK = Clustering1(TNK)
M = Clustering1(M)
Div = Clustering1(Div)
```

##TNK
```{r}
for(i in geneSet$Markers.TNK){
      print(FeaturePlot(TNK,i,cols =  col_orange))
}
TNK = RenameIdents(TNK,
                     '0' = "NK",
                     '2' = "NK",
                     '8' = "NK",
                     '12' = "NK",
                     '1' = "T_CD8",
                     '7' = "T_CD8",
                     '13' = "T_CD4",
                     '6' = "T_CD4_Foxp3",
                     '10' = "T_GD",
                     '3' = "Mix",
                     '4' = "Doublet",
                     '11' = "Doublet",
                     '9' = "LQ",
                     '5' = "LQ",
                     '14' = "LQ"
                   )
TNK$Identity.Celltype = Idents(TNK)

Mix = subset(TNK, idents = "Mix")
Mix = Clustering1(Mix)
Mix = RenameIdents(Mix,
                   '0' = "T_GD",
                   '1' = "T_CD4",
                   '2' = "T_CD8",
                   '3' = "Mix2",
                   '4' = "LQ",
                   '5' = "T_CD4",
                   '6' = "Mix2",
                   '7' = "Mix2"
                   )
Mix$Identity.Celltype = Idents(Mix)

Mix2 = subset(Mix,idents = "Mix2")
Mix2 = Clustering1(Mix2 , res =1.5)
Mix2 = RenameIdents(Mix2, 
                    '0' = "T_GD",
                    '1' = "T_CD8",
                    '2' = "T_CD4",
                    '3' = "T_CD4",
                    '4' = "T_CD8",
                    '5' = "T_CD4",
                    '6' = "T_CD4",
                    '7' = "LQ",
                    '8' = "T_GD",
                    '9' = "T_CD8",
                    '10' = "T_CD4")
Mix2$Identity.Celltype = Idents(Mix2)

tmp1 = TNK[[]] %>% dplyr::select(Identity.Celltype) %>% filter(!Identity.Celltype == "Mix")
tmp2 = Mix[[]] %>% dplyr::select(Identity.Celltype) %>% filter(!Identity.Celltype == "Mix2")
tmp3 = Mix2[[]] %>% dplyr::select(Identity.Celltype)
tmp =rbind(tmp1,tmp2,tmp3)
tmp1 = tmp$Identity.Celltype
names(tmp1) = rownames(tmp)
TNK = AddMetaData(TNK, tmp1, "Identity.Celltype")
Idents(TNK) = TNK$Identity.Celltype
```

##TIM + DC
```{r}
Idents(M) = M$seurat_clusters
M = RenameIdents(M,
                     '0' = "TIM_C1qa",
                     '1' = "TIM_Vcan",
                     '2' = "TIM_Vcan",
                     '3' = "TIM_Vcan",
                     '4' = "TIM_Vcan",
                     '5' = "cDC2",
                     '6' = "cDC1",
                     '7' = "pDC",
                     '8' = "TIM_C1qa",
                     '9' = "Doublet",
                     '10' = "mregDC",
                     '11' = "TIM_C1qa",
                     '12' = "LQ"     )
M$Identity.Celltype = Idents(M)
DimPlot(M)
```


```{r}
Vcan = subset(M, idents = "TIM_Vcan")
Vcan = Clustering1(Vcan)
Idents(Vcan) = Vcan$seurat_clusters
Vcan = RenameIdents(Vcan, 
                     '0' = "TIM_C1qa",
                     '1' = "TIM_Vcan",
                     '2' = "TIM_Vcan",
                     '3' = "TIM_Vcan",
                     '4' = "Mix",
                     '5' = "TIM_Vcan",
                     '6' = "TIM_C1qa",
                     '7' = "TIM_C1qa"
                    )
Vcan$Identity.Celltype = Idents(Vcan)

Mix = subset(Vcan, idents ="Mix")
Mix = Clustering1(Mix)
Mix = RenameIdents(Mix,'0' = "TIM_C1qa",'1' = "TIM_Vcan",'2' = "Mix", '3' ="TIM_Vcan")
Mix$Identity.Celltype = Idents(Mix)

Mix2 = subset(Mix, idents = "Mix")
Mix2 = Clustering1(Mix2)
Mix2 = RenameIdents(Mix2,'0' = "TIM_Vcan",'1' = "TIM_Vcan",'2' = "TIM_C1qa", '3' ="TIM_Vcan")
Mix2$Identity.Celltype = Idents(Mix2)

tmp0 = M[[]] %>% dplyr::select(Identity.Celltype) %>% filter(!Identity.Celltype == "TIM_Vcan")
tmp1 = Vcan[[]] %>% dplyr::select(Identity.Celltype) %>% filter(!Identity.Celltype == "Mix")
tmp2 = Mix[[]] %>% dplyr::select(Identity.Celltype) %>% filter(!Identity.Celltype == "Mix")
tmp3 = Mix2[[]] %>% dplyr::select(Identity.Celltype)
tmp = rbind(tmp0, tmp1,tmp2,tmp3)

tmp1 = tmp$Identity.Celltype
names(tmp1) = rownames(tmp)

M = AddMetaData(M, tmp1, "Identity.Celltype")
Idents(M) = M$Identity.Celltype
```



##Div
```{r}
DimPlot(Div,label=T)
Idents(Div) = Div$RNA_snn_res.0.3
Div = RenameIdents(Div,
                     '0' = "TIM_C1qa",
                     '1' = "TIM_C1qa",
                     '2' = "T_CD8",
                     '3' = "Fibroblast",
                     '4' = "NK",
                     '5' = "Doublet",
                     '6' = "TIM_Vcan",
                     '7' = "TIM_C1qa",
                     '8' = "T_CD4_Foxp3",
                     '9' = "TIM_C1qa",
                     '10' = "LQ"
                   )
Div$Identity.Celltype = Idents(Div)
```

Idents(Div) = Div$RNA_snn_res.0.3
Div = RenameIdents(Div,
                     '0' = "TIM_C1qa_Dividing",
                     '1' = "TIM_C1qa_Dividing",
                     '2' = "T_CD8_Dividing",
                     '3' = "Fibroblast_Dividing",
                     '4' = "NK_Dividing",
                     '5' = "Doublet",
                     '6' = "TIM_Vcan_Dividing",
                     '7' = "TIM_C1qa_Dividing",
                     '8' = "T_CD4_Foxp3_Dividing",
                     '9' = "TIM_C1qa_Dividing",
                     '10' = "LQ"
                   )
Div$Identity.Subtype1 = Idents(Div)

#RenameIdents
```{r}
LC$Identity.Celltype = LC$Identity.Lineage
tmp1 = LC[[]] %>% dplyr::select(Identity.Celltype) %>% filter(!Identity.Celltype %in% c("TNK","Myeloid","DC","Dividing"))
tmp2 = M[[]] %>% dplyr::select(Identity.Celltype) 
tmp3 = TNK[[]] %>% dplyr::select(Identity.Celltype) 
tmp4 = Div[[]] %>% dplyr::select(Identity.Celltype) 
tmp = rbind(tmp1,tmp2,tmp3,tmp4)
tmp$Identity.Celltype %>% unique()
tmp1 = tmp$Identity.Celltype
names(tmp1) = rownames(tmp)
LC = AddMetaData(LC, tmp1, "Identity.Celltype")
Idents(LC) = LC$Identity.Celltype
LC = RenameIdents(LC, 'T_CD4_Foxp3' = "Treg")
LC$Identity.Celltype = Idents(LC)
LC$Identity.Celltype = factor(LC$Identity.Celltype, levels = c("NK","T_CD8","T_CD4","Treg","T_GD","TAN","TIM_C1qa","TIM_Vcan","cDC1","cDC2","mregDC","pDC","B_cell","Fibroblast","Minor","Doublet","LQ"))
Idents(LC) = LC$Identity.Celltype
DimPlot(LC,label=T)
```

```{r}
NK = subset(LC, idents = "NK")
NK = Clustering1(NK)
DimPlot(NK,label =T)
geneSet$Markers.NK = c("Cd3e","Trdc","Trac","Csf1r","Nkg7","Ccl5","Bach2","Il18rap","Ccl3","Klf2","Gzme","Gzmc","Xcl1","Ifitm1","Ifitm2","Rora","Ikzf2","Nme1","Gzmb","Mki67","Hmgb2","Top2a","Klra4","Klra9","Mcm3","Mcm5","Mcm6","Isg15","Ifi203","Ifi44","Cd3e","Trac","Hist1h2ae")
for(i in geneSet$Markers.NK){
  print(FeaturePlot(NK, i, cols = col_orange))
}
Idents(NK) = NK$RNA_snn_res.0.3
NK = RenameIdents(NK,
                  '0' = "NK_Ccl5",
                  '3' = "NK_Ccl5",
                  '2' = "NK_Xcl1",
                  '1' = "NK_Gzmc",
                  '5' = "NK_Klra8",
                  '7' = "NK_Isg15",
                  '4' = "NK_Dividing",
                  '6' = "NK_Dividing",
                  '8' = "T_CD8_Dividing")
NK$Identity.Subtype1 = Idents(NK)
Idents(NK) = NK$RNA_snn_res.0.3
NK = RenameIdents(NK,
                  '0' = "NK_Ccl5_s1",
                  '3' = "NK_Ccl5_s2",
                  '2' = "NK_Xcl1",
                  '1' = "NK_Gzmc",
                  '5' = "NK_Klra8",
                  '7' = "NK_Isg15",
                  '4' = "NK_Dividing_s1",
                  '6' = "NK_Dividing_s2",
                  '8' = "T_CD8_Dividing_s2")
NK$Identity.Subtype2 = Idents(NK)
Idents(NK) = NK$RNA_snn_res.0.3
NK = RenameIdents(NK,
                  '0' = "NK",
                  '3' = "NK",
                  '2' = "NK",
                  '1' = "NK",
                  '5' = "NK",
                  '7' = "NK",
                  '4' = "NK_Dividing",
                  '6' = "NK_Dividing",
                  '8' = "T_CD8_Dividing")
NK$Identity.Celltype2 = Idents(NK)
DimPlot(NK,label=T)
```

```{r}
CD8 = subset(LC, idents = "T_CD8")
CD8 = Clustering1(CD8)
Idents(CD8) = CD8$RNA_snn_res.0.3
CD8 = RenameIdents(CD8,
                   '3' = "T_CD8_Tcf7",
                   '4' = "T_CD8_Tcf7",
                   '0' = "T_CD8_Havcr2",
                   '5' = "T_CD8_Isg",
                   '8' = "T_CD8_Ifng",
                   '1' = "T_CD8_Dividing",
                   '2' = "T_CD8_Dividing",
                   '6' = "T_CD8_Dividing",
                   '7' = "Doublet",
                   '9' = "LQ")
CD8$Identity.Subtype1 = Idents(CD8)
Idents(CD8) = CD8$RNA_snn_res.0.3
CD8 = RenameIdents(CD8,
                   '3' = "T_CD8_Tcf7_s1",
                   '4' = "T_CD8_Tcf7_s2",
                   '0' = "T_CD8_Havcr2",
                   '5' = "T_CD8_Isg",
                   '8' = "T_CD8_Ifng",
                   '1' = "T_CD8_Dividing_s1",
                   '2' = "T_CD8_Dividing_s2",
                   '6' = "T_CD8_Dividing_s3",
                   '7' = "Doublet",
                   '9' = "LQ")
CD8$Identity.Subtype2 = Idents(CD8)
Idents(CD8) = CD8$RNA_snn_res.0.3
CD8 = RenameIdents(CD8,
                   '3' = "T_CD8",
                   '4' = "T_CD8",
                   '0' = "T_CD8",
                   '5' = "T_CD8",
                   '8' = "T_CD8",
                   '1' = "T_CD8_Dividing",
                   '2' = "T_CD8_Dividing",
                   '6' = "T_CD8_Dividing",
                   '7' = "Doublet",
                   '9' = "LQ")
CD8$Identity.Celltype2 = Idents(CD8)
DimPlot(CD8,label=T)

```
```{r}
Treg = subset(LC, idents = "Treg")
Treg = Clustering1(Treg)
tmp = FindAllMarkers(Treg, max.cells.per.ident = 200)
tmp %>% group_by(cluster) %>% top_n(n=30, wt=avg_log2FC)
geneSet$Markers.CD4 = c("Stat5b","Aff1","Aff3","Bach2","Prkca","Tox","Runx1","Klf2","Ikzf3","Col3a1","Csf1r","Ifitm1","Ifitm2","Il2ra","Runx2","Bcl2","Sdf4","Lag3","Cd200","Pdcd1","Ifng")
geneSet$Markers.Treg = c("Cd3d","Cd4","Cd8a","Csf1r","Mki67","Foxp3","Il2ra","Stat5b","Tnfrsf9","mt-Co1","Malat1") 
Idents(Treg) = Treg$RNA_snn_res.0.3
Treg = RenameIdents(Treg,
                    '0' = "Treg",
                    '1' = "Treg",
                    '2' = "Treg",
                    '4' = "Treg_Dividing",
                    '5' = "Treg_Dividing",
                    '6' = "T_CD8_Foxp3",
                    '3' = "LQ"
                    )
Treg$Identity.Subtype1 = Idents(Treg)
Idents(Treg) = Treg$RNA_snn_res.0.3
Treg = RenameIdents(Treg,
                    '0' = "Treg_s1",
                    '1' = "Treg_s2",
                    '2' = "Treg_s3",
                    '4' = "Treg_Dividing_s1",
                    '5' = "Treg_Dividing_s2",
                    '6' = "T_CD8_Foxp3",
                    '3' = "LQ"
                    )
Treg$Identity.Subtype2 = Idents(Treg)
Idents(Treg) = Treg$RNA_snn_res.0.3
Treg = RenameIdents(Treg,
                    '0' = "Treg",
                    '1' = "Treg",
                    '2' = "Treg",
                    '4' = "Treg_Dividing",
                    '5' = "Treg_Dividing",
                    '6' = "T_CD8",
                    '3' = "LQ"
                    )
Treg$Identity.Celltype2 = Idents(Treg)
```



```{r}
C1qa = subset(LC, idents = c("TIM_C1qa"))
C1qa = Clustering1(C1qa,dist = 0.1, spread = 2 )
tmp1 = FindAllMarkers(C1qa, max.cells.per.ident = 200)
tmp1 %>% filter(pct.2 < 0.3) %>% group_by(cluster) %>% top_n(n=30, wt=avg_log2FC)
geneSet$Markers.C1qa =  c("Csf1r","Csf3r","Mki67","C1qa","Adgre1","Vcan","Spp1","S100a8","Axl","Gas6","Il1b","Isg15","Arg1","Vegfa","Retnla","Ptger4","Ptgs1","Ptgs2","Cd24a","Ndrg1","Ccl8","Clec10a","Cxcl9")
Idents(C1qa) =  C1qa$RNA_snn_res.0.3
C1qa = RenameIdents(C1qa,
                    '0' = "TIM_C1qa_Fcrls",
                    '1' = "TIM_C1qa_Cd24a",
                    '3' = "TIM_C1qa_Isg",
                    '7' = "TIM_C1qa_Ndrg1",
                    '2' = "TIM_C1qa_Cxcl9",
                    '8' = "TIM_C1qa_Clec10a",
                    '5' = "TIM_C1qa_Dividing_s1",
                    '6' = "TIM_C1qa_Dividing_s2",
                    '4' = "TIM_C1qa_Dividing_s3",
                    '9' = "LQ")
C1qa$Identity.Subtype2 = Idents(C1qa)
Idents(C1qa) =  C1qa$RNA_snn_res.0.3
C1qa = RenameIdents(C1qa,
                    '0' = "TIM_C1qa",
                    '1' = "TIM_C1qa",
                    '3' = "TIM_C1qa",
                    '7' = "TIM_C1qa",
                    '2' = "TIM_C1qa",
                    '8' = "TIM_C1qa",
                    '5' = "TIM_C1qa_Dividing",
                    '6' = "TIM_C1qa_Dividing",
                    '4' = "TIM_C1qa_Dividing",
                    '9' = "LQ")
C1qa$Identity.Celltype2 = Idents(C1qa)
C1qa$Identity.Subtype1 = Idents(C1qa)

DotPlot(C1qa, features = geneSet$Markers.C1qa )+Dot_axis90A + scale_ig
```

```{r}
Vcan = subset(LC, idents = "TIM_Vcan")
Vcan = Clustering1(Vcan,dist = 0.1, spread = 2 )
tmp2 = FindAllMarkers(Vcan, max.cells.per.ident = 200)
tmp2 %>% group_by(cluster) %>% top_n(n=30, wt=avg_log2FC)
tmp2 %>% filter(pct.2 < 0.3) %>% group_by(cluster) %>% top_n(n=30, wt=avg_log2FC)
geneSet$Markers.Vcan =  c("Csf1r","Csf3r","Mki67","C1qa","Adgre1","Vcan","Spp1","Il7r","Cxcl1","Cxcl3","Il1a","Tnfrsf9","Isg15","Cxcl9","H2-DMb1","Clec12a","Axl","Isg15","Ifit2","Cx3cr1")



Vcan = RenameIdents(Vcan,
                    '0' = "TIM_Vcan_Cxcl3",
                    '1' = "TIM_Vcan_Ifi202b",
                    '4' = "TIM_Vcan_Isg",
                    '2' = "TIM_Vcan_Cd244",
                    '3' = "TIM_Vcan_Cxcl9",
                    '5' = "TIM_Vcan_Cx3cr1",
                    '6' = "LQ")
Vcan$Identity.Subtype2 = Idents(Vcan)
Idents(Vcan) = Vcan$RNA_snn_res.0.3
Vcan = RenameIdents(Vcan,
                    '0' = "TIM_Vcan",
                    '1' = "TIM_Vcan",
                    '4' = "TIM_Vcan",
                    '2' = "TIM_Vcan",
                    '3' = "TIM_Vcan",
                    '5' = "TIM_Vcan",
                    '6' = "LQ")
Vcan$Identity.Subtype1 = Idents(Vcan)
Vcan$Identity.Celltype2 = Idents(Vcan)
DotPlot(Vcan, features = c("C1qa","Adgre1","Vcan") )

```




```{r}
Tan = subset(LC, idents = "TAN")
Tan = Clustering1(Tan)
Tan = RenameIdents(Tan,
                   '0' = "TAN-PMN_s1",
                   '1' = "TAN-PMN_s1",
                   '2' = "TAN-PMN_s2",
                   '3' = "TAN-PMN_s1",
                   '4' = "TAN-PMN_s1",
                   '5' = "TAN-PMN_s1",
                   '6' = "TAN-PMN_s2",
                   '7' = "TAN-PMN_s1")
Tan$Identity.Celltype2= Idents(Tan)
Tan$Identity.Subtype1= Idents(Tan)
Tan$Identity.Subtype2= Idents(Tan)
DimPlot(Tan,label =T)

```


```{r}
tmp1 = LC[[]] %>% dplyr::select(Identity.Celltype) %>% filter(!Identity.Celltype %in% c("NK","T_CD8","Treg","TIM_C1qa","TIM_Vcan","TAN"))
tmp1$Identity.Celltype2 = tmp1$Identity.Celltype
tmp1$Identity.Subtype1 = tmp1$Identity.Celltype
tmp1$Identity.Subtype2 = tmp1$Identity.Celltype

tmp2 = NK[[]]  %>% dplyr::select(Identity.Celltype,Identity.Celltype2,Identity.Subtype1,Identity.Subtype2)
tmp3 = CD8[[]]  %>% dplyr::select(Identity.Celltype,Identity.Celltype2,Identity.Subtype1,Identity.Subtype2)
tmp4 = C1qa[[]]  %>% dplyr::select(Identity.Celltype,Identity.Celltype2,Identity.Subtype1,Identity.Subtype2)
tmp5 = Vcan[[]]  %>% dplyr::select(Identity.Celltype,Identity.Celltype2,Identity.Subtype1,Identity.Subtype2)
tmp6 = Tan[[]]  %>% dplyr::select(Identity.Celltype,Identity.Celltype2,Identity.Subtype1,Identity.Subtype2)
tmp7 = Treg[[]]  %>% dplyr::select(Identity.Celltype,Identity.Celltype2,Identity.Subtype1,Identity.Subtype2)
tmp = rbind(tmp1,tmp2,tmp3,tmp4,tmp5,tmp6,tmp7)
tmp
tmp1 = tmp$Identity.Celltype2
names(tmp1) = rownames(tmp)
LC = AddMetaData(LC, tmp1, "Identity.Celltype2")

tmp1 = tmp$Identity.Subtype1
names(tmp1) = rownames(tmp)
LC = AddMetaData(LC, tmp1, "Identity.Subtype1")

tmp1 = tmp$Identity.Subtype2
names(tmp1) = rownames(tmp)
LC = AddMetaData(LC, tmp1, "Identity.Subtype2")

Idents(LC) = LC$Identity.Celltype2
write.csv(sort(unique(LC$Identity.Celltype2)),"LC.Identity.Celltype2.csv")
write.csv(sort(unique(LC$Identity.Subtype1 )),"LC.Identity.Subtype1.csv")
write.csv(sort(unique(LC$Identity.Subtype2 )),"LC.Identity.Subtype2.csv")

tmp =read.csv("LC.Identity.Celltype2.modified.csv")$x
setdiff(unique(LC$Identity.Celltype2), tmp)
LC$Identity.Celltype2 = factor(LC$Identity.Celltype2, levels = tmp)

tmp =read.csv("LC.Identity.Subtype1.modified.csv")$x
setdiff(unique(LC$Identity.Subtype1), tmp)
LC$Identity.Subtype1 = factor(LC$Identity.Subtype1, levels = tmp)

tmp =read.csv("LC.Identity.Subtype2.modified.csv")$x
setdiff(unique(LC$Identity.Subtype2), tmp)
LC$Identity.Subtype2 = factor(LC$Identity.Subtype2, levels = tmp)
saveRDS(LC, file = "LC.Identity.Subtype2.230404.rds")

Idents(LC) = LC$Identity.Subtype2
DimPlot(LC)
```

saveRDS(LC, file = "LC.230330.rds")
saveRDS(M, file = "LC.M.230330.rds")
saveRDS(TNK, file = "LC.TNK.230330.rds")
saveRDS(Div, file = "LC.Div.230330.rds")

saveRDS(NK, file = "LC.NK.Identity.Subtype.230403.rds")
saveRDS(CD8, file = "LC.CD8.Identity.Subtype.230403.rds")
saveRDS(Treg, file = "LC.Treg.Identity.Subtype.230403.rds")
saveRDS(Vcan, file = "LC.Vcan.Identity.Subtype.230403.rds")
saveRDS(Tan, file = "LC.Tan.Identity.Subtype.230403.rds")
saveRDS(C1qa, file = "LC.C1qa.Identity.Subtype.230403.rds")

```{r}
LC <- readRDS("/rshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/Mouse/RDS/LC.Identity.Subtype2.230404.rds")
Idents(LC) = LC$Identity.Celltype2
tmp = setdiff(levels(Idents(LC)), c("Fibroblast","Minor","Doublet","LQ" ))
LC = subset(LC, idents = tmp)
LC = Clustering1(LC)
DimPlot(LC)
saveRDS(LC,"/rshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/Mouse/RDS/LC.rmLQ.230405.rds")
```

#DE (LLC1)
DE.LLC.Celltype.230419.r
```{r}
library(Seurat)
library(harmony)
library(tidyverse)
options(future.globals.maxSize = 100000 * 1024^2)

LC = readRDS(file = "/rshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/Mouse/RDS/LC.rmLQ.230405.rds")
LLC = subset(LC, orig.ident == "LLC1")
LC = 0
Idents(LLC) = "Batch"
B1 <- subset(LLC, idents = "Day6")
B2 <- subset(LLC, idents = "Day1.5")
B3 <- subset(LLC, idents = "Day14")

LLC = 0

DE.LLC= list()
DE.LLC$Day1.5 = list()
DE.LLC$Day6 = list()
DE.LLC$Day14 = list()
Idents(B1) = B1$Identity.Celltype
Idents(B2) = B2$Identity.Celltype
Idents(B3) = B3$Identity.Celltype

tmp = setdiff(levels(Idents(B1)), c("Fibroblast","Minor","Doublet","LQ" ))
print(tmp)
for(i in tmp ){
      print(i)
      tryCatch({
            tmp1 = subset(B1,idents = i)
            tmp2 = subset(B2,idents = i)
            tmp3 = subset(B3,idents = i)
            Idents(tmp1) = "Condition"
            Idents(tmp2) = "Condition"
            Idents(tmp3) = "Condition"
            DE1 = list()
            tryCatch({DE1[["EP2i-Control"]] = FindMarkers(tmp1, ident.1 = "EP2i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            tryCatch({DE1[["EP4i-Control"]] = FindMarkers(tmp1, ident.1 = "EP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            tryCatch({DE1[["EP2iEP4i-Control"]] = FindMarkers(tmp1, ident.1 = "EP2iEP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            DE.LLC$Day6[[i]] = DE1 
            
            DE2 = list()
            tryCatch({DE2[["EP2iEP4i-Control"]] = FindMarkers(tmp2, ident.1 = "EP2iEP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            DE.LLC$Day1.5[[i]] = DE2
            
            
            DE3 = list()
            tryCatch({DE3[["EP2iEP4i-Control"]] = FindMarkers(tmp3, ident.1 = "EP2iEP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            DE.LLC$Day14[[i]] = DE3
            
            saveRDS(DE.LLC,"//home/siwakorn/Mouse/RDS/DE.LLC.Celltype.230419.rds")
      }, error = function(e){print(e)})
}
```

DE.LLC.230405.r
```{r}
library(Seurat)
library(harmony)
library(tidyverse)
options(future.globals.maxSize = 100000 * 1024^2)

LC = readRDS(file = "/rshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/Mouse/RDS/LC.rmLQ.230405.rds")
LLC = subset(LC, orig.ident == "LLC1")
LC = 0
Idents(LLC) = "Batch"
B1 <- subset(LLC, idents = "Day6")
B2 <- subset(LLC, idents = "Day1.5")
B3 <- subset(LLC, idents = "Day14")

LLC = 0

DE.LLC= list()
DE.LLC$Day1.5 = list()
DE.LLC$Day6 = list()
DE.LLC$Day14 = list()
Idents(B1) = B1$Identity.Celltype2
Idents(B2) = B2$Identity.Celltype2
Idents(B3) = B3$Identity.Celltype2

tmp = setdiff(levels(Idents(B1)), c("Fibroblast","Minor","Doublet","LQ" ))
print(tmp)
for(i in tmp ){
      print(i)
      tryCatch({
            tmp1 = subset(B1,idents = i)
            tmp2 = subset(B2,idents = i)
            tmp3 = subset(B3,idents = i)
            Idents(tmp1) = "Condition"
            Idents(tmp2) = "Condition"
            Idents(tmp3) = "Condition"
            DE1 = list()
            tryCatch({DE1[["EP2i-Control"]] = FindMarkers(tmp1, ident.1 = "EP2i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            tryCatch({DE1[["EP4i-Control"]] = FindMarkers(tmp1, ident.1 = "EP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            tryCatch({DE1[["EP2iEP4i-Control"]] = FindMarkers(tmp1, ident.1 = "EP2iEP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            DE.LLC$Day6[[i]] = DE1 
            
            DE2 = list()
            tryCatch({DE2[["EP2iEP4i-Control"]] = FindMarkers(tmp2, ident.1 = "EP2iEP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            DE.LLC$Day1.5[[i]] = DE2
            
            
            DE3 = list()
            tryCatch({DE3[["EP2iEP4i-Control"]] = FindMarkers(tmp3, ident.1 = "EP2iEP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            DE.LLC$Day14[[i]] = DE3
            
            saveRDS(DE.LLC,"//home/siwakorn/Mouse/RDS/DE.LLC.Celltype2.230405.rds")
      }, error = function(e){print(e)})
}
```


DE.LLC.Subtype1.230406.r
```{r}
library(Seurat)
library(harmony)
library(tidyverse)
options(future.globals.maxSize = 100000 * 1024^2)

LC = readRDS(file = "/rshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/Mouse/RDS/LC.rmLQ.230405.rds")
LLC = subset(LC, orig.ident == "LLC1")
LC = 0
Idents(LLC) = "Batch"
B1 <- subset(LLC, idents = "Day6")
B2 <- subset(LLC, idents = "Day1.5")
B3 <- subset(LLC, idents = "Day14")

LLC = 0

DE.LLC= list()
DE.LLC$Day1.5 = list()
DE.LLC$Day6 = list()
DE.LLC$Day14 = list()
Idents(B1) = B1$Identity.Subtype1
Idents(B2) = B2$Identity.Subtype1
Idents(B3) = B3$Identity.Subtype1

tmp = setdiff(levels(Idents(B1)), c("Fibroblast","Minor","Doublet","LQ" ))
print(tmp)
for(i in tmp ){
      print(i)
      tryCatch({
            tmp1 = subset(B1,idents = i)
            tmp2 = subset(B2,idents = i)
            tmp3 = subset(B3,idents = i)
            Idents(tmp1) = "Condition"
            Idents(tmp2) = "Condition"
            Idents(tmp3) = "Condition"
            DE1 = list()
            tryCatch({DE1[["EP2i-Control"]] = FindMarkers(tmp1, ident.1 = "EP2i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            tryCatch({DE1[["EP4i-Control"]] = FindMarkers(tmp1, ident.1 = "EP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            tryCatch({DE1[["EP2iEP4i-Control"]] = FindMarkers(tmp1, ident.1 = "EP2iEP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            DE.LLC$Day6[[i]] = DE1 
            
            DE2 = list()
            tryCatch({DE2[["EP2iEP4i-Control"]] = FindMarkers(tmp2, ident.1 = "EP2iEP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            DE.LLC$Day1.5[[i]] = DE2
            
            
            DE3 = list()
            tryCatch({DE3[["EP2iEP4i-Control"]] = FindMarkers(tmp3, ident.1 = "EP2iEP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            tryCatch({DE3[["Depletion-Control"]] = FindMarkers(tmp3, ident.1 = "Depletion", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            DE.LLC$Day14[[i]] = DE3
            
            saveRDS(DE.LLC,"//home/siwakorn/Mouse/RDS/DE.LLC.Subtype1.230405.rds")
      }, error = function(e){print(e)})
}

```

#DE (CT26)
DE.CT26.Celltype.230405.r
```{r}
library(Seurat)
library(harmony)
library(tidyverse)
options(future.globals.maxSize = 100000 * 1024^2)

LC = readRDS(file = "/rshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/Mouse/RDS/LC.rmLQ.230405.rds")
CT26 = subset(LC, orig.ident == "CT26")
LC = 0
Idents(CT26) = "Batch"
B1 <- subset(CT26, idents = "Batch1")
B2 <- subset(CT26, idents = "Batch2")
CT26= 0
DE.CT26= list()
DE.CT26$Batch1 = list()
DE.CT26$Batch2 = list()

Idents(B1) = B1$Identity.Celltype2
Idents(B2) = B2$Identity.Celltype2

tmp = setdiff(levels(Idents(B1)), c("Fibroblast","Minor","Doublet","LQ" ) )
print(tmp)
for(i in tmp ){
      print(i)
      tryCatch({
            tmp1 = subset(B1,idents = i)
            tmp2 = subset(B2,idents = i)
            Idents(tmp1) = "Condition"
            Idents(tmp2) = "Condition"
            DE2 = list()
            tryCatch({DE2[["EP4i-Control"]] = FindMarkers(tmp2, ident.1 = "EP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            tryCatch({DE2[["PD1i-Control"]] = FindMarkers(tmp2, ident.1 = "PD1i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            tryCatch({DE2[["PD1iEP4i-Control"]] = FindMarkers(tmp2, ident.1 = "PD1iEP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            tryCatch({DE2[["PD1iEP4i-PD1i"]] = FindMarkers(tmp2, ident.1 = "PD1iEP4i", ident.2 = "PD1i", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            tryCatch({DE2[["PD1iEP4i-EP4i"]] = FindMarkers(tmp2, ident.1 = "PD1iEP4i", ident.2 = "EP4i", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            DE.CT26$Batch2[[i]] = DE2
            
            DE1 = list()
            tryCatch({DE1[["EP4i-Control"]] = FindMarkers(tmp1, ident.1 = "EP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            DE.CT26$Batch1[[i]] = DE1
            
            saveRDS(DE.CT26,"//home/siwakorn/Mouse/RDS/DE.CT26.Celltype2.230405.rds")
      }, error = function(e){print(e)})
}

```

DE.CT26.Subtype1.230406.r
```{r}
library(Seurat)
library(harmony)
library(tidyverse)
options(future.globals.maxSize = 100000 * 1024^2)

LC = readRDS(file = "/rshare1/ZETTAI_path_WA_slash_home_KARA/home/siwakorn/Mouse/RDS/LC.rmLQ.230405.rds")
CT26 = subset(LC, orig.ident == "CT26")
LC = 0
Idents(CT26) = "Batch"
B1 <- subset(CT26, idents = "Batch1")
B2 <- subset(CT26, idents = "Batch2")
CT26= 0
DE.CT26= list()
DE.CT26$Batch1 = list()
DE.CT26$Batch2 = list()

Idents(B1) = B1$Identity.Subtype1
Idents(B2) = B2$Identity.Subtype1

tmp = setdiff(levels(Idents(B1)), c("Fibroblast","Minor","Doublet","LQ" ) )
print(tmp)
for(i in tmp ){
      print(i)
      tryCatch({
            tmp1 = subset(B1,idents = i)
            tmp2 = subset(B2,idents = i)
            Idents(tmp1) = "Condition"
            Idents(tmp2) = "Condition"
            DE2 = list()
            tryCatch({DE2[["EP4i-Control"]] = FindMarkers(tmp2, ident.1 = "EP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            tryCatch({DE2[["PD1i-Control"]] = FindMarkers(tmp2, ident.1 = "PD1i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            tryCatch({DE2[["PD1iEP4i-Control"]] = FindMarkers(tmp2, ident.1 = "PD1iEP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            tryCatch({DE2[["PD1iEP4i-PD1i"]] = FindMarkers(tmp2, ident.1 = "PD1iEP4i", ident.2 = "PD1i", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            tryCatch({DE2[["PD1iEP4i-EP4i"]] = FindMarkers(tmp2, ident.1 = "PD1iEP4i", ident.2 = "EP4i", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            DE.CT26$Batch2[[i]] = DE2
            
            DE1 = list()
            tryCatch({DE1[["EP4i-Control"]] = FindMarkers(tmp1, ident.1 = "EP4i", ident.2 = "Control", min.pct = 0.01 , logfc.threshold = 0.01)}, error = function(e){print(e)})
            DE.CT26$Batch1[[i]] = DE1
            
            saveRDS(DE.CT26,"//home/siwakorn/Mouse/RDS/DE.CT26.Subtype1.230405.rds")
      }, error = function(e){print(e)})
}

```


